%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Hack The North 2022 | Managed with Git} % Organisation
    {\underline{DrawBot | \href{https://devpost.com/software/drawbot-ulof5z}{Link}}} % Project
    {Waterloo, ON} % Location
    {Sept. 2022 - Sept. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of project
        \item {A hackathon project that turns speech descriptions into real drawings}
        \item {\textbf{Assembly AI} turns speech into text prompts for \textbf{Stable Diffusion}}
        \item {Generated image is translated to vector format and sent to Raspberry PI, which controls a gantry system to create the drawing}
        \item {\textbf{Fusion 360} used to create models for hardware aspect of project}
        % \item {\textbf{Technical Skills:} Stable Diffusion, Python, Javascript, React.js, Fusion 360.}
        % \item {\textbf{Soft Skills:} Time Management, Teamwork, Presentation skills, Communication.}
      \end{cvitems}
    }


%---------------------------------------------------------
  \cventry
    {Hack The North 2021 | \textbf{Best Use of Google Cloud} | \textbf{Best Entrepreneurship Hack} | Managed with Git} % Organisation
    {\underline{Hive-HQ - Winner | \href{https://devpost.com/software/hive-hq}{Link}}} % Project
    {Ottawa, ON} % Location
    {Sept. 2021 - Sept. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of project
        \item {An AI-powered, multi-target tracking system that identifies high traffic areas in public spaces. The project empowers small business owners by bringing AI analytics to small business owners.}
        \item {\textbf{YOLOv5} model was loaded onto \textbf{PyTorch} to recognize and annotate individuals.}
        \item {Built using \textbf{Google Cloud}, matrix perspective transformations, \textbf{React.js}, \textbf{OpenCV}, \textbf{Pytorch}, and \textbf{YOLOv5}.}
        % \item {\textbf{Technical Skills:} Python, PyTorch, OpenCV, Google Cloud, AWS, React.js.}
        % \item {\textbf{Soft Skills:} Time Management, Teamwork, Presentation skills, Communication.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {MLH Hacky Birthday 2021 | \textbf{Third Overall} | Managed with Git} % Organisation
    {\underline{MaskPass - Winner | \href{https://devpost.com/software/mlh-birthday-ads}{Link}}} % Project
    {Ottawa, ON} % Location
    {July 2021 - July 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of project
        \item {A door that utilizes cameras and AI to discern if an individual has a mask on or not to open a conditional door.}
        \item {A system that recognizes a customer’s mask status - no mask, mask on, and states in-between}
        \item {Leverages \textbf{cloud computing} to be viable on low-power devices.}
        \item {built using \textbf{TensorFlow} for CV, \textbf{Flask server} for custom API, \textbf{VEX} radio for motor control of door}
        % \item {\textbf{Technical Skills:} TensorFlow, Flask, Arduino, VEX}
        % \item {\textbf{Soft Skills:} Time Management, Teamwork, Presentation skills, Communication.}
      \end{cvitems}
    }

  \cventry
    {Personal Project} % Organisation
    {\underline{Heimdall Personal Dashboard | \href{https://heimdall.lefan.me}{Link}}} % Project
    {Ottawa, ON} % Location
    {July 2021 - now} % Date(s)
    {
      \begin{cvitems} % Description(s) of project
        \item {A self hosted site using Cloudflare \& Oracle servers that present many self hosted services}
        % \item {Nginx reverse-proxy is used to proxy running docker instances to their respective subdomains on site}
        % \item {Built using \textbf{SWAG}, \textbf{Docker}, \textbf{Oracle Cloud}, \textbf{Cloudflare}}
        \item {\textbf{Technical Skills:} Docker, Nginx, Authelia, MongoDB, AWS lambda, Networking \& Port Management}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
